A Comparision of Bootstrap Methods

### 2022-12-01 project/PaperTemplate/paper.Rmd
more sim

  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}

  # use the data set to create the bootstrapped distribution (1 bootstrap and then keep replicated statistic of interest)
  # like 2000 times

  #use that bootstrap distribution as follows to test for the intervals

  # see how many times the true value lies inside the interval --> first do one and then show the actual intervals

```{r}
set.seed(495)
simulation_reps <- 30
trueparameter <- 4
n <- 100

@@

#ci <- as.data.frame(ci) %>%
#  rename("Standard Interval" = V1, "Percentile Interval" = V2, "BC Interval" = V3, "BCa Interval" = V4, "Studentized Interval" = V5)

output

ci_prop <- colSums(ci)/simulation_reps
ci_prop

@@

```{r}
Y <- rgamma(5, shape = 8, scale = 2)
Y

>>>>

  output <- list(standard_interval, percentile_interval, bc_interval, bca_interval, t_interval)
  names(output) <- c("Standard Interval", "Percentile Interval", "BC Interval", "BCa Interval", "Studentized Interval")
  output
}
```

```{r}
run_simulation_gamma <- function(num_reps, sample_size){
  set.seed(495)
  simulation_reps <- num_reps
  trueparameter <- 4
  n <- sample_size

@@

  ci_prop <- colSums(ci)/simulation_reps
  ci_prop
}

@@

```{r}
#10 100 500 1000
data2 <- matrix(nrow = 3, ncol = 6)

for (i in 1:3) {
  output2 <- run_simulation_gamma(10, 10^i)
  data2[i, 1] <- 10^i
  data2[i, 2] <- output2[1]
  data2[i, 3] <- output2[2]
  data2[i, 4] <- output2[3]
  data2[i, 5] <- output2[4]
  data2[i, 6] <- output2[5]
}

output3 <- as.data.frame(data2) %>% 
  rename("sample_size" = V1, "standard" = V2, "percentile" = V3, "BC" = V4, "BCa" = V5, "studentized" = V6)

output4 <- output3 %>%
  pivot_longer(cols = 2:6, names_to = "method", values_to = "prop")

ggplot(data = output4, aes(x = sample_size, y = prop, color = method))+
  geom_point() +
  geom_line()

Y <- rgamma(5, shape = 8, scale = 2)
Y
